### 2023-12-18 documentation/thesis/thesis_document.tex
more thesis

@@

After it is very easy for users to carry out measurements using the
\gls{cli}, the next logical step is to analyse the recorded data. This
can involve one or several hundred data records. Again, the procedure
for the user is to write their own evaluation scripts using the
\gls{mrp}-library. This is particularly useful for complex analyses or
custom algorithms, but not necessarily for simple standard tasks such as
bias compensation or graphical plot outputs. For this purpose, a further
\gls{cli} application was created, which enables the user to create and
execute complex evaluation pipelines for measurement data without
programming. The example\ref{example_measurement_analysis_pipeline.png}
shows a typical measurement data analysis pipeline, which consists of
the following steps:

@@

stage apply_bias_offset:
  function: apply_sensor_bias_offset
  parameters:
    bias_readings: stage import_bias_reading
    readings_to_calibrate: stage import_readings

stage apply_temp_compensation:
  function: apply_temperature_compensation
  parameters:
    readings_to_calibrate: stage import_readings

@@

\begin{itemize}
\tightlist
\item
  blöcke erleutern insbesondere stage
\item
  wie calltree gebildet
\end{itemize}

>>>>

After it is very easy for users to carry out measurements using the
\gls{cli}, the next logical step is to analyse the recorded data. This
can involve one or several hundred data records. Again, the procedure
for the user is to write their own evaluation scripts using the
\gls{mrp}-library. This is particularly useful for complex analyses or
custom algorithms, but not necessarily for simple standard tasks such as
bias compensation or graphical plot outputs.

@@

For this purpose, a further \gls{cli} application was created, which
enables the user to create and execute complex evaluation pipelines for
measurement data without programming. The
example\ref{example_measurement_analysis_pipeline.png} shows a typical
measurement data analysis pipeline, which consists of the following
steps:

@@

stage apply_bias_offset:
  function: apply_sensor_bias_offset
  parameters:
    bias_readings: stage import_bias_reading # USE RESULT FROM FUNCTION import_bias_reading
    readings_to_calibrate: stage import_readings

stage apply_temp_compensation:
  function: apply_temperature_compensation
  parameters:
    readings_to_calibrate: stage import_readings # USE RESULT FROM FUNCTION import_readings

@@

Each pipeline step is divided into \passthrough{\lstinline!stages!},
which contain a name, the function to be executed and its parameters.
The various steps are then linked by using the
\passthrough{\lstinline!stage <name>!} as the input parameter of the
next function to be executed (see comments in
\ref{lst:mrpuddp_example_yaml}). It is therefore also possible to use
the results of one function in several others without them directly
following each other. The disadvantages of this system are as the
following:

\begin{itemize}
\tightlist
\item
  No loops can be created
\item
  Complex determination of the execution sequence of the steps
\end{itemize}

To determine the order of the pipeline steps, the parser script created
converts them into one problem of the graph theories. Each step
represents a node in the graph and the steps referred to by the input
parameter form the edges.

After several simplification steps, determination of possible start
steps and repeated traversal, the final execution sequence can be
determined in the form of a call
tree\ref{Result_step_execution_tree_from_user_defined_processing_pipeline_example.png}.

\begin{figure}
\centering
\includegraphics{./generated_images/border_Result_step_execution_tree_from_user_defined_processing_pipeline_example.png}
\caption{Result step execution tree from user defined processing
pipeline example
\label{Result_step_execution_tree_from_user_defined_processing_pipeline_example.png}}
\end{figure}

The individual steps are then executed along the graph. The intermediate
results and the final result are saved for later use.

\begin{itemize}
\tightlist
\item
  vorteile erleutern kurz
\end{itemize}
